### 2019-09-04 manuscript/manuscript.tex
updated plots, etc

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on sign permuting the allele frequency changes. In
    subfigure A, windowed covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are
    separated by $k=2 \times 10$ generations and in subfigure B the covariances
    are separated by $k=4 \times 10$ generations; each $k$ is an off-diagonal
    from the variance diagonal of the temporal covariance matrix (see cartoon
    of upper-triangle of covariance matrix in subfigures A and B, where the
    first diagonal is the variance, and the dark gray indicates which
    off-diagonal of the covariance matrix is plotted in the histograms). C: The
    lower and upper tail probabilities of the observed windowed covariances, at
    20\% and 80\% quintiles of the empirical neutral null distribution, for
    varying time between allele frequency changes (i.e. which off-diagonal
    $k$). The confidence intervals are  $95\%$ block-bootstrap confidence
    interval, and the light gray dashed line indicates the 20\% tail
    probability expected under the neutral null.}

@@

  \caption{The variance and covariances calculated in 100kb genomic windows
    plotted against average depth in a window before and after bias correction.
    Each panel has a least-squares estimate between the variance and
    covariance, and the average depth. Overall, the bias correction corrects
    sampling bias in both the variance and covariance such that the
    relationship with depth is constant. Colors indicate the different
    chromosomes of \emph{D. simulans}; we have excluded the X chromosome
    (yellow points) and chromosome 4 points (green points to far right) from
    the regression due to large differences in average coverage.}

@@

  \caption{}
  \label{suppfig:barghi-cross-validation-binsize}
\end{figure}

@@

We were concerned that this might be due to a flaw in our methods. To address
this concern, we first ensured that our temporal-covariance matrix bias
correction was working as expected. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure XXX) as
expected. We then re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B).

@@

>>>>

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on sign permuting the allele frequency changes. The
    bin number is 88, chosen by cross validation (Supplementary Materials
    \ref{suppfig:barghi-cross-validation-binsize}). In subfigure A, windowed
    covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are separated by $k=2 \times
    10$ generations and in subfigure B the covariances are separated by $k=4
    \times 10$ generations; each $k$ is an off-diagonal from the variance
    diagonal of the temporal covariance matrix (see cartoon of upper-triangle
    of covariance matrix in subfigures A and B, where the first diagonal is the
    variance, and the dark gray indicates which off-diagonal of the covariance
    matrix is plotted in the histograms). C: The lower and upper tail
    probabilities of the observed windowed covariances, at 20\% and 80\%
    quintiles of the empirical neutral null distribution, for varying time
    between allele frequency changes (i.e. which off-diagonal $k$). The
  confidence intervals are  $95\%$ block-bootstrap confidence interval, and the
light gray dashed line indicates the 20\% tail probability expected under the
neutral null.}

@@

  \caption{The variance and covariances from the \textcite{Barghi2019-qy}
    study, calculated in 100kb genomic windows plotted against average depth in
    a window before and after bias correction.  Each panel has a least-squares
    estimate between the variance and covariance, and the average depth.
    Overall, the bias correction corrects sampling bias in both the variance
    and covariance such that the relationship with depth is constant. Colors
    indicate the different chromosomes of \emph{D. simulans}; we have excluded
  the X chromosome (yellow points) and chromosome 4 points (green points to far
right) from the regression due to large differences in average coverage.}

@@

  \caption{We chose the binsize used in the histograms of Figure
  \ref{fig:figure-3} via an analytic expression for the cross-validation risk,
based on the equation 6.16 of (\cite{Wasserman2006-jl}, p. )}

  \label{suppfig:barghi-cross-validation-binsize}
\end{figure}

@@

We were concerned that this might be due to a flaw in our methods. To address
this concern, we first ensured that our temporal-covariance matrix bias
correction was working as expected. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure
\ref{suppfig:bergland-correction}) as expected. We then re-analyzed the data of
\parencite{Bergland2014-ij} using the same seasonal fluctuating model as the
original paper. This model is a Binomial logit-linked GLM fit per-locus, where
the Spring/Fall seasons are encoded as a dummy variable, and are regressed on
the frequency data. We use the same binomial weighting procedure as
\textcite{Bergland2014-ij}, where the weights are determined by the effective
number of chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t + d_t)$ ($n_t$ and
$d_t$ are the number of diploid individuals and the read depth at timepoint
$t$, respectively). We fit this model on all loci marked as used in the VCF
provided with the \textcite{Bergland2014-ij} study (doi:10.5061/dryad.v883p).
Overall, our p-values for the Wald test for each locus closely match those of
the original paper (Pearson correlation coefficient 0.98, p-value < $2.2 \times
10^{-16}$; see Supplementary Figure \ref{suppfig:bergland-pvalue-comparison}
A), and the histograms of the p-values are nearly identical (Supplementary
Figure \ref{suppfig:bergland-pvalue-comparison} B).

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/bergland-correction-plot.pdf}

  \caption{The variance and covariances from the \texticite{Bergland2014-ij}
    study, calculated in 100kb genomic windows plotted against average depth in
    a window before and after bias correction. Each panel has a least-squares
    estimate between the variance and covariance, and the average depth.
    The bias correction procedure is correcting sampling bias in both the variance
    and covariance such that the relationship with depth is constant. Colors
    indicate the different chromosomes of \emph{D. melanogaster}; we have
    excluded the X chromosome (yellow points; chromosome 4 was not in the
    original study) from the regression due to large differences in average
    coverage.}

  \label{suppfig:bergland-correction}
\end{figure}
